How to Avoid OOTA Without Really Trying

### 2024-09-01 paper/ootavacuous.tex
paper/ootavacuous: Remove "Additional Litmus Tests" appendix
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Most of the examples in this paper involve simple semantic dependencies
connecting a single load to a single store.
One exception appears in
Appendix~\ref{app:Additional Litmus Tests},
but this section will present a more difficult example.

@@

\subsection{Additional Litmus Tests}
\label{app:Additional Litmus Tests}

This section lists a few other litmus tests of interest:

\begin{itemize}
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-two-source.litmus}
	shows multiple overlapping OOTA cycles.
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-non-lb.litmus}
	shows that OOTA cycles are not confined to the load-buffering (LB)
	pattern.
\item	The litmus test at
	\url{https://github.com/paulmckrcu/oota/blob/master/litmus/oota-invent-int-load.litmus}
	shows another invented-load scenario loosely based on
	Figure~\ref{lst:OOTA Cycle}
	on
	page~\pageref{lst:OOTA Cycle}.
	See Appendix~\ref{app:Inventing Atomic Loads}
	for more discussion on this topic.
\end{itemize}

>>>>

Most of the examples in this paper involve simple semantic dependencies
connecting a single load to a single store,
but this section will present a more difficult example.

@@
